Katana Paper Additions

### 2010-02-25 paper1/additions.tex
made a few last notes on paper additions

\textcolor{red}{We \emph{are} handling relocations for code patches,
  but full support for the PLT is currently \emph{not} implemented
  (it's soon on my to-do list)}

\textcolor{red}{The addition of new symbols is not actually fully
  supported at the moment, as my first couple examples only patched
  existing variables. I could get this working in an hour or two
  though}

@@

\subsection{Our Patch Object Format}
Our Patch Object (PO) format is an ELF-based
format. Figure \ref{fig:elfheaders} shows the sections contained in a
simple patch. \texttt{.text.new} and \texttt{.rodata.new} are of
course the new code and supporting
\begin{wrapfigure}{l}{0.4\textwidth}
{\footnotesize
\begin{verbatim}
  Section Headers:
    [Nr] Name              Type          
    [ 0]                   NULL          
    [ 1] .strtab           STRTAB        
    [ 2] .symtab           SYMTAB        
    [ 3] .text.new         PROGBITS      
    [ 4] .rodata.new       PROGBITS      
    [ 5] .rela.text.new    RELA          
    [ 6] .debug_info       PROGBITS      
    [ 7] .debug_abbrev     PROGBITS      
    [ 8] .debug_frame      PROGBITS      
    [ 9] .rel.debug_info   REL           
    [10] .rel.debug_frame  REL           
\end{verbatim}
}
\caption{Headers for the PO}
\label{fig:elfheaders}
\vspace{-10pt}
\end{wrapfigure}
constants to inject. \texttt{.rela.text.new} allows \texttt{.text.new}
to be properly relocated after it is adjusted. While System V based
systems use only relocation sections of type \texttt{SHT\_REL}, we
chose to use \texttt{SHT\_RELA} in our patch objects because they make
addends much easier to keep track of as we relocate from patched
binary to patch object to patched process in memory. This is all
really nothing new, storing ELF sections to be injected in-memory has
been done before in other systems. What is new in our patch object is
the inclusion of DWARF sections. The \texttt{.debug\_info} section in
an ordinary executable program contains a tree of DIEs (Debugging
Information Entities) with information about every type, variable, and
procedure in each compilation unit in the program. In a patch object,
we store information only about the procedures and variables which
have changed. This of course includes storing the type information for
changed variables. An example of the DWARF DIE information contained
in a patch can be seen in Figure \ref{fig:dies}.

>>>>

\textcolor{red}{We \emph{are} handling relocations for code patches,
  including support for the PLT}

@@

\subsection{Our Patch Object Format}
Our Patch Object (PO) format is an ELF-based
format. Figure \ref{fig:elfheaders} shows the sections contained in a
simple patch. \texttt{.text.new} and \texttt{.rodata.new} are of
course the new code and supporting
\begin{wrapfigure}{l}{0.4\textwidth}
{\footnotesize
\begin{verbatim}
  Section Headers:
    [Nr] Name              Type          
    [ 0]                   NULL          
    [ 1] .strtab           STRTAB        
    [ 2] .symtab           SYMTAB        
    [ 3] .text.new         PROGBITS      
    [ 4] .rodata.new       PROGBITS      
    [ 5] .rela.text.new    RELA          
    [ 6] .debug_info       PROGBITS      
    [ 7] .debug_abbrev     PROGBITS      
    [ 8] .debug_frame      PROGBITS      
    [ 9] .rel.debug_info   REL           
    [10] .rel.debug_frame  REL           
\end{verbatim}
}
\caption{Headers for the PO}
\label{fig:elfheaders}
\vspace{-10pt}
\end{wrapfigure}
constants to inject. \texttt{.rela.text.new} allows \texttt{.text.new}
to be properly relocated after it is adjusted. While System V based
systems use only relocation sections of type \texttt{SHT\_REL}, we
chose to use \texttt{SHT\_RELA} in our patch objects because they make
addends much easier to keep track of as we relocate from patched
binary to patch objectp to patched process in memory. This is all
really nothing new, storing ELF sections to be injected in-memory has
been done before in other systems. What is new in our patch object is
the inclusion of DWARF sections. The \texttt{.debug\_info} section in
an ordinary executable program contains a tree of DIEs (Debugging
Information Entities) with information about every type, variable, and
procedure in each compilation unit in the program. In a patch object,
we store information only about the procedures and variables which
have changed. This of course includes storing the type information for
changed variables. An example of the DWARF DIE information contained
in a patch can be seen in Figure \ref{fig:dies}.
